### 2019-08-29 upper.tex
Recent observations

This justifies taking a different approach to repartitioning (see Section PPLA).

>>>>

This justifies taking a different approach to repartitioning then bounding the repartition cost in $O(k^2\cdot \ell^2)$ algorithm (described in Section ``A simple upper bound'' in the DISC paper).
As the cost of a specific repartition is $\Omega(k^2)$, then the cost of DET during a single phase is: for each of $O(k \cdot l)$ edges revealed, we already have the cost $O(k^2)$ (precisely, $O(min\{k^2, k\ell\})$, and the competitive ratio would be $O(k^3\cdot \ell)$. \maciek{This would be an improvement in terms of $\ell$ still, but no hopes for $O(k\ell)$ algorithm just by improving the rebalancing analysis}
